Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-04-26 review_response/review_response.tex

\thispagestyle{plain}

\begin{center}
	{\Large\myTitle} \vspace{0.5cm} \\
%	{\large\myJournal} \vspace{0.5cm} \\
	\today \vspace{0.5cm} \\
	\myAuthors \\
	\url{\myEmail} \vspace{1cm} \\
	\myDept
\end{center}

\tableofcontents

\begin{abstract}
We submitted an earlier version of this paper to 
\emph{Transactions on Spatial Algorithms and Systems}
on July 27, 2018.
According to the concerns of the reviewers,
the Editor-in-Chief, Walid Aref, rejected that version.
He encouraged us to address the concerns and 
``submit as a new paper''.

We thank the anonymous reviewers for their comments.
These comments were very helpful for us to improve our paper. 
In this document, 
we provide detailed responses to each of the reviewers' comments. 
The following list summarizes our most important changes:
\begin{itemize}
    \item  An NP-hardness proof has been added.
    \item  The illustration of the exponential lower bound has been improved.
    \item  The approach based on integer linear programming 
    has been moved to the appendix.
    \item  Several comments concerning the applied compactness measures 
    have been incorporated.
\end{itemize}
\end{abstract}

### 2020-03-31 area_agg_seq_tsas.tex
some small improvements

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polyglines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

@@

\begin{figure}[tb]
\centering
\includegraphics{AreaAgg_example}
\caption{The input and a possible output of an aggregation sequence 
	for an instance of our problem}
\label{fig:AreaAgg_example}
\end{figure}

With the same motivation, 
a strategy of hierarchical schemes has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree (GAP-tree).
This tree can be constructed if only the larger-scale map is given
\citep{vanOosterom1995Development} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, in a greedy fashion.  
If we insist on finding a sequence that is optimal 
according to some global measure,
the problem becomes complicated.

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Note that although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence land-cover maps.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=3]{AreaAgg_Preliminaries}
\caption{The subdivision graph~$G_\mathrm{S}$. 
	The nodes of the graph are the subdivisions. 
	There is an arc	from subdivision~\Pnode 
	to subdivision~${P}_{t+1,j}$ 
	if~${P}_{t+1,j}$ is the result of 
	an aggregating step from~\Pnode.}
\label{fig:AreaAgg_SubdivisionName}
\end{figure}

@@

\subsection{Exponential lower bound}
\label{sec:AreaAgg_Exponential}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we use a row of~$n$ land-cover areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangular patches,
and the goal map is simply the union of the~$n$ patches.
The patches have area 
sizes~$
%\left( 
100 + \frac{1}{n}, 99+ \frac{2}{n}, 
100 + \frac{3}{n}, 99+ \frac{4}{n}, \ldots, 
99 + \frac{n-1}{n}, \text{and~} 101 
%\right)
$, 
from left to right.
According to our rule, we always 
aggregate the smallest patch with one of its neighbors.
Therefore, in the first~$k$ steps from the start map,
we aggregate every other patch with one of its neighbors.
However, we do not know which one is the right choice
at each of the steps,
in order to minimize our costs (see \sect\ref{sec:AreaAgg_CostFunctions}).
We have to try both of the two choices,
aggregating with the left patch or with the right one.
As a result, there are~$2^k = 2^{(n-1)/2}$ subdivisions 
in layer~$L_{k+1}$.
That is to say, the size of subdivision graph~$G_\mathrm{S}$
has exponential lower bound.

@@

Our idea is to obtain an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal 
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that our inputs are only
subdivisions~$\Pstart$ and~$\Pgoal$
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
We generate a subdivision (node) only when we want to visit it.

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs
%\parencite[e.g.,][\sect25.2]{Cormen2009},
(e.g., \textcite[\sect25.2]{Cormen2009}),
however, will explore the whole graph, which has exponential size.
The \Astar algorithm can be seen as 
a refinement of Dijkstra's algorithm, 
which for a user-specified given source 
computes shortest paths to all other nodes in an edge-weighted graph
\parencite{Dijkstra1959}. 
Even when using Dijkstra's algorithm 
to compute only a single shortest path to a user-specified destination, 
a large number of nodes need to be explored. 
The same holds for shortest-path algorithms 
that make use of a topological order of the nodes 
in a directed acyclic graph. 
Compared to these algorithms, 
the \Astar algorithm can greatly reduce the number of explored nodes.
The challenge in our work was to tune the A* algorithm such that it
explores only a small fraction of the graph.

@@

Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d_\mathrm{type}(T(u),T(v))}{d_\mathrm{type\_max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We use~$A_R$ and~$d_\mathrm{type\_max}$ 
to normalize the cost of type change. 
Constant~$d_\mathrm{type\_max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies, for each pair~$(T_1,T_2)$ of types, 
cost~$d_\mathrm{type}(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}); 
\textcite[\chap2]{Choudhary1992Elements}
shows the definition of a metric.
A metric distance is symmetric, 
which is different from the asymmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance from \emph{road} to \emph{building} is~$0$.

@@

We use the compactness definition of \citet{Frolov1975}, 
i.e., the compactness value for a patch, say,~$u$ is
\begin{equation}
\label{eq:comp}
c(u)=\frac{2 \sqrt{\pi A_u}}{l_u},
\end{equation}
where~$A_u$ and~$l_u$ are 
the area and the perimeter. 
For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
the set of the patches' compactnesses.

We wish to maximize the sum of the average compactnesses 
over all intermediate maps,
while our objective will be
minimizing a cost function.
To adapt the average compactness to our methods, 
we define and minimize a cost related to compactness.
Recalling that there are~$n-s+1$ patches at time~$s$,
we define the cost of compactness for subdivision~\Psnode as
\begin{equation}
\label{eq:f_comp}
f_\mathrm{comp}(\Psnode)=
\frac{1-\frac{1}{n-s+1} \sum_{c\in C(\Psnode)}c}{n-2},
\end{equation}
where we use values~$n-s+1$ and~$n-2$ to normalize 
the cost of compactness.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{The reduction for our NP-hardness proof.
    The dashed polygon in (c) shows 
    that the vertices are merged.}
\label{fig:AreaAgg_Reduction}
\end{figure}

@@

A motivation for the greedy algorithm is that 
a very similar iterative algorithm has been used by
\textcite{vanOosterom1995Development} 
for constructing the tGAP data structure.
However, we have to make minor modifications to ensure that 
the computed aggregation sequence ends with the goal map that, 
in our situation, is given as a part of the input.
We use our greedy algorithm as a benchmark
so that we are able to see 
whether the \Astar algorithm or the ILP-based algorithm 
indeed perform better.

@@

We tested our method on a dataset 
from the German topographic database ATKIS DLM~50. 
The dataset represents the place 
``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
Our start map is the result of collapsing areas 
by \citet[\chap6]{haunert2008f}.
The start map has~$5{,}537$ polygons. 
Our goal map was generalized from the start map 
by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
The goal map has~$734$ polygons, 
which means that there are~$N=734$ regions.
The distribution of region sizes is shown in 
\fig\ref{fig:AreaAgg_NumRegion}.
%
We used a tree-based method introduced by 
\citet{Rada1989SemanticMetric} 
to define the distances of the types;
the distance is the ``number of edges'' that
we need to travel from one node to another node in the tree of 
type hierarchy\footnote{More information 
    about land-cover types can be found at 
%	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
	Accessed: Nov 1, 2017.}
(see \fig\ref{fig:AreaAgg_TypeDistances}). 
For example, the distance from type \emph{village}
to type \emph{fence} is~$2$, 
to type \emph{street} is~$4$, and
to type \emph{farm land} is~$6$.
In this tree, the maximum distance is~$6$, 
which means~$d_\mathrm{type\_max}=6$ for \eq\ref{eq:f_type}.
According to \citet{Rada1989SemanticMetric}, 
the resulting cost function for type change is a metric.

@@

As illustrated in \sect\ref{sec:AreaAgg_Combining},
we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
which is a combination of the costs 
of type change and compactness (see \eq\ref{eq:g_1}).
For \Astar, we overestimated 
whenever we could not find a solution after 
having visited~$W$ nodes 
(see \sect\ref{sec:AreaAgg_AStar}).
We tried~$W=200{,}000$ and~$W=400{,}000$
(if we could use more main memory, 
then we could test by using some larger~$W$). 
The results are shown in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
%
Comparing to \Astar, 
the greedy algorithm visited 
fewer nodes and arcs in graph~$G_\mathrm{S}$ 
and used much less time.
However, \Astar managed to find solutions with 
lower total cost,~$117.3$ (or~$117.2$), 
which is~$2.8\%$ less than 
the total cost of the greedy algorithm,~$120.7$.
%
When~$W=200{,}000$, we are sure that 
we have found optimal solutions 
for~$702$ of the~$734$ regions ($95.6\%$),
while the greedy algorithm solved 
only~$408$ ($55.6\%$) to optimality;
see column \#OS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
For the other~$32$ regions, 
both algorithms have found feasible solutions 
(see column \#FS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
Although some of the feasible solutions may also be optimal,
we cannot verify that only from the cost values.

@@

Among all the instances that were solved to optimality by \Astar
in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
and~\ref{sec:AreaAgg_CaseStudy2}),
region~$358$ (marked in \tab\ref{tab:CostsInDetail})
is the largest one.
In both experiments, the cost of type change is~$0.044$.
The optimal aggregation sequences for this region
obtained by using costs~$g_1$ and~$g_2$
are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
We, however, noticed some unpleasant aggregates.
The step from~$8$ patches to~$7$ patches 
when using cost function~$g_1$ is a bad move
(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
Instead we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
Using cost function~$g_2$, we had a similar problem. 
The subdivision with~$7$ patches is such an example,
where we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
In an earlier version of this paper \parencite[see][]{Peng2017AStar},
we tried a combination of minimizing type changes 
and maximizing the sum of the smallest compactness values, 
over the whole sequence.
For that objective, we had a similar problem as 
in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
This problem, however, can be fixed easily 
by forbidding two patches to aggregate 
if their common boundary is too short.
Moreover, there are two more possible solutions.
First, we could integrate the shared length
into our cost function, as did by \textcite{vanOosterom1995Development}.
Second, we could weight the cost of shape more heavily
(i.e., increasing weight factor~$\lambda$ of \eqs\ref{eq:g_1} and~\ref{eq:g_2}).
According to our experiences, 
the weight factor that we applied defines a reasonable trade-off 
between the different conflicting objectives, 
when considering a solution as a whole. 
However, we are far from claiming that 
the applied weight factor has been optimally chosen. 
This would probably require a user study.

\begin{figure}[h!tb]
\centering
\includegraphics[page=1]{AreaAgg_CaseStudy2}
\caption{Some intermediate subdivisions of region~$358$ 
	obtained by \Astar with different cost functions.
	The numbers indicate the numbers of patches.
    The step from $8$ patches to $7$ patches 
    when using cost function~$g1$ is a bad move; see figure (b). 
    Instead, we expect the result of figure (a). 
    Using cost function~$g2$, we had a similar problem. 
    The subdivision with $7$ patches is such an example, 
    where we expect the result of figure (c).
}
\label{fig:AreaAgg_CaseStudy2_Rg358}
\end{figure}

@@

Our second set of variables is used to compute the
cost of type change.  We introduce
\begin{flalign*}
&\eqquadVariable
\embrd[V]{y_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1\}, \forall p,o,r \in P&
\end{flalign*}
with the intended meaning~$y_{t,p,o,r}=1$ if and only if 
polygon~$p$ is assigned to center~$o$ at time~$t-1$ 
and assigned to center~$r$ at time~$t$ 
(see \fig\ref{fig:AreaAgg_Variables}).
Specifically, case~$y_{t,p,o,o}=1$ means that
polygon~$p$ is assigned to the same center 
at times~$t-1$ and~$t$.

@@

\mypar{Aggregation involving a smallest patch}
In order to make sure that 
each of our aggregation steps involves a smallest patch,
we need another type of variable,~$w_{t,o}$.
Recall that the intended meaning of~$w_{t,o}=1$ is 
if and only if 
polygon~$o$ is the center of 
a smallest patch at time~$t$.
We will use this to enforce that
this patch is involved in the aggregation step 
from time~$t$ to~$t+1$.
At any time~$t$, 
we pick exactly one smallest patch (there can be many) 
and aggregate it with one of its neighbors;
we do not care whether or not the neighbor is a smallest one.
Therefore, we have
\begin{flalign}
\label{eq:CstrSOneSmallest}
&\eqquadConstraintW
\embrd[S]{\sum_{o\in P}w_{t,o}} =
\embld[T]{1} \inquad 
\forall t \in {T}\setminus \{n\}.&
\end{flalign}

>>>>

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes map features (e.g., polyglines and polygons) 
in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
We believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_Preliminaries}
\caption{The input and a possible output for an instance of 
our problem.}
\label{fig:AreaAgg_example}
\end{figure}

With the same motivation, 
a strategy of hierarchical schemes has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree (GAP-tree).
This tree can be constructed if only the larger-scale map is given
\citep{vanOosterom2005} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, in a greedy fashion.  
If we insist on finding a sequence that is optimal 
according to some global measure,
the problem becomes complicated.

We assume that there exist many-to-one relationships 
between the areas of the start map and the areas of the goal map.
This assumption is based on the fact that many algorithms 
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
vanSmaalen2003,Oehrlein2017Aggregation}
result in many-to-one relationships
when aggregating land-cover areas.
Their inputs and generalized results together
can be used as our inputs.
However, we should not use those algorithms
to generate a sequence of maps at different scales
because those algorithms do not take into account 
the consistence between the generated maps.
We use both a start map and a goal map instead of using only the start map
because our generated maps at intermediate scales should be able to
benefit from a goal map with high quality.

We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, by the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single smaller scale, 
given a land-cover map at a larger scale.
Although \textcite{HaunertWolff2010AreaAgg}
attain results of high quality, 
they do not produce a sequence of land-cover maps.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=3]{AreaAgg_Preliminaries}
\caption{The subdivision graph, $G_\mathrm{S}$. 
	The nodes of the graph are the subdivisions. 
	There is an arc	from subdivision~\Pnode 
	to subdivision~${P}_{t+1,j}$ 
	if~${P}_{t+1,j}$ is the result of 
	an aggregation step from~\Pnode.}
\label{fig:AreaAgg_SubdivisionName}
\end{figure}

@@

\subsection{Exponential lower bound}
\label{sec:AreaAgg_Exponential}
We now analyze the size of subdivision graph~$G_\mathrm{S}$.
Our analysis is inspired by \textcite{Keane1975Size},
where we use a row of~$n$ land-cover areas.
In our instance
(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
the start map consists of~$n=2k+1$ rectangular patches,
and the goal map is simply the union of the~$n$ patches.
The patches have area 
sizes~$
%\left( 
100 + \frac{1}{n}, 99+ \frac{2}{n}, 
100 + \frac{3}{n}, 99+ \frac{4}{n}, \ldots, 
99 + \frac{n-1}{n}, \text{and~} 101 
%\right)
$, 
from left to right.
According to our rule, we always 
aggregate the smallest patch with one of its neighbors.
Therefore, in the first~$k$ steps from the start map,
we aggregate every other patch with one of its neighbors.
However, we do not know which one is the right choice
at each of the steps
in order to minimize our costs (see \sect\ref{sec:AreaAgg_CostFunctions}).
We have to try both of the two choices,
aggregating with the left patch or with the right one.
As a result, there are~$2^k = 2^{(n-1)/2}$ subdivisions 
in layer~$L_{k+1}$.
That is to say, the size of subdivision graph~$G_\mathrm{S}$
has exponential lower bound.

@@

Our idea is to obtain an optimal aggregation sequence through 
computing a path with minimum weight, from the start to the goal 
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since graph~$G_\mathrm{S}$ can be huge.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that our inputs are only
subdivisions~$\Pstart$ and~$\Pgoal$
(see \fig\ref{fig:AreaAgg_SubdivisionName}).
We generate a subdivision (node) only when we want to visit it.

In directed acyclic graphs, shortest paths can be found slightly faster 
than in general directed or undirected graphs.
An off-the-shelf shortest-path algorithm for directed acyclic graphs
%\parencite[e.g.,][\sect25.2]{Cormen2009},
(e.g., \textcite[\sect25.2]{Cormen2009}),
however, will explore the whole graph, which has exponential size.
The \Astar algorithm can be seen as 
a refinement of Dijkstra's algorithm, 
which for a user-specified given source 
computes shortest paths to all other nodes in an edge-weighted graph
\parencite{Dijkstra1959}. 
Even when using Dijkstra's algorithm 
to compute only a single shortest path to a user-specified destination, 
a large number of nodes need to be explored. 
The same holds for shortest-path algorithms 
that make use of a topological order of the nodes 
in a directed acyclic graph. 
Compared to these algorithms, 
the \Astar algorithm can greatly reduce the number of explored nodes.
The challenge in our work was to tune the \Astar algorithm such that 
it explores only a small fraction of the graph.

@@

Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d_\mathrm{type}(T(u),T(v))}{d_\mathrm{type\_max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We use~$A_R$ and~$d_\mathrm{type\_max}$ 
to normalize the cost of type change. 
Constant~$d_\mathrm{type\_max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies
cost~$d_\mathrm{type}(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}).
A metric distance is symmetric, 
which is different from the asymmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance from \emph{road} to \emph{building} is~$0$.

@@

We use the compactness definition of \citet{Frolov1975}, 
i.e., the compactness value of a patch, say,~$u$ is
\begin{equation}
\label{eq:comp}
c(u)=\frac{2 \sqrt{\pi A_u}}{l_u},
\end{equation}
where~$A_u$ and~$l_u$ are 
the area and the perimeter. 
For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
the set of the patches' compactness values.

We wish to maximize the sum of the average compactness values 
over all intermediate maps,
while our objective will be
minimizing a cost function.
To adapt the average compactness to our methods, 
we define and minimize a cost related to compactness.
Recalling that there are~$n-s+1$ patches at time~$s$,
we define the cost of compactness for subdivision~\Psnode as
\begin{equation}
\label{eq:f_comp}
f_\mathrm{comp}(\Psnode)=
\frac{1-\frac{1}{n-s+1} \sum_{c\in C(\Psnode)}c}{n-2},
\end{equation}
where we use values~$n-s+1$ and~$n-2$ to normalize 
the cost of compactness.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=1]{AreaAgg_NPHard}
\caption{The reduction for our NP-hardness proof.
    The dashed polygon in (c) shows 
    the merged vertices.}
\label{fig:AreaAgg_Reduction}
\end{figure}

@@

A motivation for the greedy algorithm is that 
a very similar iterative algorithm has been used by
\textcite{vanOosterom2005} 
for constructing the tGAP data structure.
However, we have to make minor modifications to ensure that 
the computed aggregation sequence ends with the goal map that, 
in our situation, is given as a part of the input.
We use our greedy algorithm as a benchmark
so that we are able to see 
whether the \Astar algorithm or the ILP-based algorithm 
indeed perform better.

@@

We tested our method on a dataset 
from the German topographic database ATKIS DLM~50. 
The dataset represents the place 
``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
Our start map is the result of collapsing areas 
by \citet[\chap6]{haunert2008f}.
The start map has~$5{,}537$ polygons. 
Our goal map was generalized from the start map 
by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
The goal map has~$734$ polygons, 
which means that there are~$N=734$ regions.
The distribution of region sizes is shown in 
\fig\ref{fig:AreaAgg_NumRegion}.
%
We used a tree-based method introduced by 
\citet{Rada1989SemanticMetric} 
to define the distances of the types;
the distance is the ``number of edges'' that
we need to travel from one node to another node in the tree of 
type hierarchy\footnote{More information 
    about land-cover types can be found at 
	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
	Accessed: Nov 1, 2017.}
(see \fig\ref{fig:AreaAgg_TypeDistances}). 
For example, the distance from type \emph{village}
to type \emph{fence} is~$2$, 
to type \emph{street} is~$4$, and
to type \emph{farm land} is~$6$.
In this tree, the maximum distance is~$6$, 
which means~$d_\mathrm{type\_max}=6$ for \eq\ref{eq:f_type}.
According to \citet{Rada1989SemanticMetric}, 
the resulting cost function for type change is a metric.

@@

As illustrated in \sect\ref{sec:AreaAgg_Combining},
we compare the \Astar algorithm and 
the greedy algorithm using $g_1(\Pnode)$,
which is a combination of the costs 
of type change and compactness (see \eq\ref{eq:g_1}).
For \Astar, we overestimated 
whenever we could not find a solution after 
having visited~$W$ nodes 
(see \sect\ref{sec:AreaAgg_AStar}).
We tried~$W=200{,}000$ and~$W=400{,}000$
(if we could use more main memory, 
then we could test by using some larger~$W$). 
The results are shown in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
%
Comparing to \Astar, 
the greedy algorithm visited 
fewer nodes and arcs in graph~$G_\mathrm{S}$ 
and used much less time.
However, \Astar managed to find solutions with 
lower total cost,~$117.3$ (or~$117.2$), 
which is~$2.8\%$ less than 
the total cost of the greedy algorithm,~$120.7$.
%
When~$W=200{,}000$, we are sure that 
we have found optimal solutions 
for~$702$ of the~$734$ regions ($95.6\%$),
while the greedy algorithm solved 
only~$408$ ($55.6\%$) to optimality;
see column \#OS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
For the other~$32$ regions, 
both algorithms have found feasible solutions 
(see column \#FS in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
Although some of the feasible solutions may also be optimal,
we cannot verify that only from the cost values.

@@

Among all the instances that were solved to optimality by \Astar
in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
and~\ref{sec:AreaAgg_CaseStudy2}),
region~$358$ (marked in \tab\ref{tab:CostsInDetail})
is the largest one.
In both experiments, the cost of type change is~$0.044$.
The optimal aggregation sequences for this region
obtained by using costs~$g_1$ and~$g_2$
are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
We, however, noticed some unpleasant aggregates.
The step from~$8$ patches to~$7$ patches 
when using cost function~$g_1$ is a bad move
(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
Instead we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
Using cost function~$g_2$, we had a similar problem. 
The subdivision with~$7$ patches is such an example,
where we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
In an earlier version of this paper \parencite[see][]{Peng2017AStar},
we tried a combination of minimizing type changes 
and maximizing the sum of the smallest compactness values, 
over the whole sequence.
For that objective, we had a similar problem as 
in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
This problem, however, can be fixed easily 
by forbidding two patches to aggregate 
if their common boundary is too short.
Moreover, there are two more possible solutions.
First, we could integrate the shared length
into our cost function, as did by \textcite{vanOosterom2005}.
Second, we could weight the cost of shape more heavily
(i.e., increasing weight factor~$\lambda$ of \eqs\ref{eq:g_1} and~\ref{eq:g_2}).
According to our experiences, 
the weight factor that we applied defines a reasonable trade-off 
between the different conflicting objectives, 
when considering a solution as a whole. 
However, we are far from claiming that 
the applied weight factor has been optimally chosen. 
This would probably require a user study.

\begin{figure}[h!tb]
\centering
\includegraphics[page=1]{AreaAgg_CaseStudy2}
\caption{Some intermediate subdivisions of region~$358$ 
	obtained by \Astar with different cost functions.
	The numbers indicate the numbers of patches.
    The step from $8$ patches to $7$ patches 
    when using cost function~$g_1$ is a bad move; see figure (b). 
    Instead, we expect the result of figure (a). 
    Using cost function~$g_2$, we had a similar problem. 
    The subdivision with $7$ patches is such an example, 
    where we expect the result of figure (c).
}
\label{fig:AreaAgg_CaseStudy2_Rg358}
\end{figure}

@@

We use the second set of variables in order to compute the
cost of type change. We introduce
\begin{flalign*}
&\eqquadVariable
\embrd[V]{y_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1\}, \forall p,o,r \in P&
\end{flalign*}
with the intended meaning~$y_{t,p,o,r}=1$ if and only if 
polygon~$p$ is assigned to center~$o$ at time~$t-1$ 
and assigned to center~$r$ at time~$t$ 
(see \fig\ref{fig:AreaAgg_Variables}).
Specifically, case~$y_{t,p,o,o}=1$ means that
polygon~$p$ is assigned to the same center 
at times~$t-1$ and~$t$.

@@

\subsubsection{Aggregation involving a smallest patch}
In order to make sure that 
each of our aggregation steps involves a smallest patch,
we need another type of variable,~$w_{t,o}$.
Recall that the intended meaning of~$w_{t,o}=1$ is 
if and only if 
polygon~$o$ is the center of 
a smallest patch at time~$t$.
We will use this to enforce that
this patch is involved in the aggregation step 
from time~$t$ to~$t+1$.
At any time~$t$, 
we pick exactly one smallest patch (there can be many) 
and aggregate it with one of its neighbors;
we do not care whether or not the neighbor is a smallest one.
Therefore, we have
\begin{flalign}
\label{eq:CstrSOneSmallest}
&\eqquadConstraintW
\embrd[S]{\sum_{o\in P}w_{t,o}} =
\embld[T]{1} \inquad 
\forall t \in {T}\setminus \{n\}.&
\end{flalign}
